Tables

### 2020-12-18 tables.Rmd
muddling through analyses...
#9 updates to ego graphs

library(kableExtra)
library(tidyverse)
library(ggplot2)
```

@@

```{r, fig.width=3.5, fig.height=3}
ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University

plot_characteristic <- function(df, type, characteristics) {
  sub_df <- df %>% select(University, characteristics) %>%
    gather(key, value, characteristics) %>%
    mutate(value = parse_number(value))

  # colors <- sub_df$color[order(sub_df$University)]

  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))

  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
```

# Ego network graph

See Figure \@ref(fig:ego-plot).

```{r ego-plot, fig.align = 'center', out.width = '100%', fig.cap = 'Ego network'}
knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
```

>>>>

library(kableExtra)
library(tidyverse)
library(labelled)
library(ggplot2)
library(gridExtra)
```

@@

\newpage

```{r, fig.width=3.5, fig.height=3, message=FALSE}
# ggplot's default color palette
# library(scales)
# show_col(hue_pal()(4))

plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
  if (visit_count) {
    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
  }

  ordered_df <- df %>% arrange(desc(cluster), univ_name)
  univ_order <- ordered_df$univ_name
  cluster_face <- map_chr(ordered_df$cluster, function(x) if_else(as.numeric(x) %% 2 == 0, 'bold', 'plain'))

  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
    gather(key, value, characteristic) %>%
    mutate(value = parse_number(value))

  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
  sub_df$key <- factor(sub_df$key, levels = characteristic)

  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_text(face = rev(cluster_face)),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')

for (i in 1:length(type_vec)) {
  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))

  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 2))

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'), visit_count = TRUE)
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  # print(a)
  # print(b)
  # print(c)
  # print(d)
}
```

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private high schools visited by private colleges and universities"}
knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}
